---
title: "when reorder fails"
output: md_document
date: "2024-07-13"
---

I am using the "mpg" dataset included in the ggplot2 package.

```{r message=FALSE, warning=FALSE}
#load packages
library(tidyverse)
library(tidytext)
```

```{r message=FALSE, warning=FALSE}
#view data
glimpse(mpg)

```

```{r message=FALSE, warning=FALSE}
mpg %>% 
  group_by(trans) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(mapping = aes(trans, n)) +
  geom_bar(stat = "identity")
```

This plot is ok, but how about arranging the order of trans by frequency? We can use reorder.

```{r message=FALSE, warning=FALSE}
mpg %>% 
  group_by(trans) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(mapping = aes(reorder(trans, n), n)) +
  geom_bar(stat = "identity")
```

Ok, this is what we want. Let's work with a more complicated example. We want the relation between the distribution of trans varied by drv.

```{r message=FALSE, warning=FALSE}
mpg %>% 
  group_by(drv, trans) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(mapping = aes(reorder(trans, n), n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ drv, scale = "free")
```

`reorder` doesn't work well with a third-dimension variable. Use `reorder_within` (in **tidytext** package) instead

```{r message=FALSE, warning=FALSE}
mpg %>% 
  group_by(drv, trans) %>% 
  count() %>% 
  ungroup() %>% 
  ggplot(mapping = aes(reorder_within(trans, n, drv), n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ drv, scale = "free")
```

